\begin{thebibliography}{9}

\bibitem{le_calve_database_merging}
\textbf{Anne Le Calvé and Jacques Savoy (2000)},
\textit{Database Merging Strategy based on Logistic Regression},
Information Processing \& Management, Volume 36, Issue 3, 1 May 2000, Pages 341-359.

\bibitem{ngrams_authorship}
\textbf{Vlado Keselj, Fuchun Peng, Nick Cercone, Calvin Thomas (2003)},
\textit{N-Gram-based Author Profiles for Authorship Attribution},
2003 Pacific Association for Computational Linguistics.

\bibitem{bcubed}
\textbf{Enrique Amigó ́Julio Gonzalo, Javier Artiles, Felisa Verdejo (2009)},
\textit{A comparison of Extrinsic Clustering Evaluation Metrics based on Formal Constraints},
Departamento de Lenguajes y Sistemas Informaticos, UNED, Madrid, Spain, 2009.

\bibitem{automated_unsupervised}
\textbf{Robert Layton, Paul Watters and Richard Dazeley (2011)},
\textit{Automated Unsupervised Authorship Analysis using Evidence Accumulation Clustering},
2011 Natural Language Engineering 19.

\bibitem{pan11_verif}
\textbf{Shlomo Argamon and Patrick Juola (2011)},
\textit{Overview of the International Authorship Identification Competition at PAN-2011},
Authorship Verification task at PAN @ CLEF 2011.

\bibitem{comparing_compression}
\textbf{W. Oliveira Jr., E. Justino, L.S. Oliveira (2013)},
\textit{Comparing Compression Models for Authorship Attribution},
Forensic Science International 228 (2013) 100-104.

\bibitem{savoy_probability}
\textbf{Jacques Savoy (2015)},
\textit{Estimating the Probability of an Authorship Attribution},
Journal of the association for information science and technology, 2015.

\bibitem{savoy_text_representation}
\textbf{Jacques Savoy (2015)},
\textit{Text Representation Strategies: An Example With the State of the Union Addresses},
Journal of the association for information science and technology, 2015.

\bibitem{kocher_verification}
\textbf{Mirco Kocher and Jacques Savoy (2016)},
\textit{A Simple and Efficient Algorithm for Authorship Verification},
Journal of the association for information science and technology, 2016.

\bibitem{pan16}
\textbf{Efstathios Stamatatos, Michael Tschuggnall, Ben Verhoeven, Walter Daelemans, Günther Specht, Benno Stein, and Martin Potthast (2016)},
\textit{Clustering by Authorship Within and Across Documents},
Author Clustering task at PAN @ CLEF 2016.

\bibitem{bagnall_pan16}
\textbf{Douglas Bagnall (2016)},
\textit{Authorship Clustering using Multi-headed Recurrent Neural Networks},
Author Clustering task at PAN @ CLEF 2016.

\bibitem{kocher_pan16}
\textbf{Mirco Kocher (2016)},
\textit{UniNE at CLEF 2016: Author Clustering},
Author Clustering task at PAN @ CLEF 2016.

\bibitem{attribution_in_cyberspace}
\textbf{Jawwad A. Shamsi, Sherali Zeadally, Fareha Sheikh and Angelyn Flowers (2016)},
\textit{Attribution in cyberspace: techniques and legal implications},
Security and communication networks, 2016

\bibitem{st_jean}
\textbf{Dominique Labbé (2017)},
\textit{Une Expérience d’Attribution d’Auteur. Le Corpus Saint-Jean},
2017 CNRS – Université de Grenoble-Alpes.

\bibitem{ddlc}
\textbf{Dan Salvato, Team Salvato (2017)},
\textit{Doki Doki Literature Club!},
Freeware, visual novel.

\bibitem{kocher_linking}
\textbf{Mirco Kocher and Jacques Savoy (2018)},
\textit{Evaluation of Text Representation Schemes and Distance Measures for Authorship Linking},
Digital Scholarship in the Humanities, The Author(s), 2018.

\bibitem{savoy_starnone}
\textbf{Jacques Savoy (2018)},
\textit{Is Starnone really the author behind Ferrante?},
Digital Scholarship in the Humanities, Vol. 33, No. 4, 2018.

\bibitem{generations}
\textbf{OECD - Social Policy Division - Directorate of Employment, Labour and Social Affairs (2019)},
\textit{SF2.3: Age of Mothers at Child Birth and Age-specific Fertility},
2019 OECD Family Database.

\bibitem{siamese_network_pan20}
\textbf{Emir Araujo-Pino, Helena Gómez-Adorno, and Gibran Fuentes-Pineda (2020)},
\textit{Siamese Network applied to Authorship Verification},
Authorship verification task at PAN @ CLEF 2020.

\bibitem{feature_vector_pan20}
\textbf{Janith Weerasinghe and Rachel Greenstadt (2020)},
\textit{Feature Vector Difference based Neural Network and Logistic Regression Models for Authorship Verification},
Authorship verification task at PAN @ CLEF 2020.

\bibitem{unine_pan20_verif}
\textbf{Catherine Ikae (2020)},
\textit{UniNE at PAN-CLEF 2020: Author Verification},
Authorship verification task at PAN @ CLEF 2020.

\bibitem{unine_pan20_fake_news}
\textbf{Catherine Ikae, Jacques Savoy (2020)},
\textit{UniNE at PAN-CLEF 2020: Profiling Fake News Spreaders on Twitter},
Profiling Fake News Spreaders on Twitter task at PAN @ CLEF 2020.

\bibitem{overview_pan20}
\textbf{Mike Kestemont, Enrique Manjavacas, Ilia Markov, Janek Bevendorff, Matti Wiegmann, Efstathios Stamatatos, Martin Potthast, and Benno Stein (2020)},
\textit{Overview of the Cross-Domain Authorship Verification Task at PAN 2020},
Authorship verification task at PAN @ CLEF 2020.

\bibitem{savoy_stylo}
\textbf{Jacques Savoy (2020)},
\textit{Machine Learning Methods for Stylometry: Authorship Attribution and Author Profiling},
Springer Nature Switzerland AG 2020. ISBN: 978-3-030-53359-5.

%urls

\bibitem{pan_webis}
\textbf{Webis Group},
\textit{PAN@CLEF}: \url{https://pan.webis.de/} (last access: 27.05.2021),
Pan.webis.de.

\bibitem{pan16_corpus}
\textbf{Stamatatos Efstathios, Tschuggnall Michael, Verhoeven Ben, Daelemans Walter, Specht Günther, Stein Benno, Potthast Martin},
\textit{PAN16 Author Identification: Clustering}: \url{https://zenodo.org/record/3737587} (last access: 30.03.2021),
Zenodo.org.

\bibitem{pan16_clustering_site}
\textbf{Stamatatos Efstathios, Juola Patrick, Potthast Martin, Stein Benno, Verhoeven Ben},
\textit{PAN16 Author Clustering 2016}: \url{https://pan.webis.de/clef16/pan16-web/author-clustering.html} (last access: 07.04.2021),
Webis.de.

\bibitem{unine_corpus}
\textbf{University of Neuchâtel},
\textit{UNINE Corpus et sites internets}: \url{http://www.unine.ch/clc/home/Corpus.html} (last access: 30.03.2021),
Unine.ch.

%libs

\bibitem{python}
\textbf{Python},
\textit{Python is a programming language that lets you work quickly and integrate systems more effectively.}: \url{https://www.python.org/} (last access: 07.04.2021),
python.org.

\bibitem{python_standard_library}
\textbf{Python Standard Library},
\textit{Data Compression and Archiving}: \url{https://docs.python.org/3/library/} (last access: 20.04.2021),
python.org.

\bibitem{matplotlib}
\textbf{Matplotlib},
\textit{Visualization with Python}: \url{https://matplotlib.org/} (last access: 07.04.2021),
matplotlib.org.

\bibitem{numpy}
\textbf{Numpy},
\textit{The fundamental package for scientific computing with Python}: \url{https://numpy.org/} (last access: 07.04.2021),
numpy.org.

\bibitem{scipy}
\textbf{SciPy},
\textit{SciPy a Python-based ecosystem for mathematics, science, and engineering}: \url{https://www.scipy.org/} (last access: 07.04.2021),
scipy.org.

\bibitem{sklearn}
\textbf{Scikit-learn},
\textit{Machine Learning in Python}: \url{https://scikit-learn.org/} (last access: 07.04.2021),
scikit-learn.org.

\bibitem{wiki_silhouette}
\textbf{Wikipédia (en)},
\textit{Silhouette (clustering)}: \url{https://en.wikipedia.org/wiki/Silhouette_(clustering)} (last access: 16.06.2021),
wikipedia.org.

\bibitem{wiki_measures}
\textbf{Wikipédia (en)},
\textit{Evaluation measures (information retrieval)}: \url{https://en.wikipedia.org/wiki/Evaluation_measures_(information_retrieval)} (last access: 05.07.2021),
wikipedia.org.

\bibitem{wiki_f1}
\textbf{Wikipédia (en)},
\textit{F-score}: \url{https://en.wikipedia.org/wiki/F-score} (last access: 14.07.2021),
wikipedia.org.

\bibitem{jupyter}
\textbf{Project Jupyter},
\textit{To develop open-source software, open-standards, and services for interactive computing across dozens of programming languages}: \url{https://jupyter.org/} (last access: 21.05.2021),
jupyter.org.

\bibitem{bcubed_gh}
\textbf{Hugo Hromic (hhromic)},
\textit{Simple Extended BCubed implementation in Python for clustering evaluation}: \url{https://github.com/hhromic/python-bcubed} (last access: 06.05.2021),
GitHub Page.

\bibitem{adjustText}
\textbf{Ilya Flyamer (Phlya)},
\textit{A small library for automatically adjustment of text position in matplotlib plots to minimize overlaps}: \url{https://github.com/Phlya/adjustText} (last access: 06.05.2021),
GitHub Page.

\bibitem{tqdm}
\textbf{Casper da Costa-Luis (casperdcl) and Stephen Karl Larroque (lrq3000)},
\textit{A Fast, Extensible Progress Bar for Python and CLI}: \url{https://github.com/tqdm/tqdm} (last access: 17.05.2021),
GitHub Page.

\end{thebibliography}
