\subsection{Rank list evaluation metrics \label{sec:rl_eval}}

In order to know the quality of a rank list, multiple rank list evaluation metrics are used and presented in this section.
Definitions in these sections are adapted versions of the ones in Kocher and Savoy's \textit{Evaluation of text representation schemes and distance measures for authorship linking}~\cite{kocher_linking}.
The presented metrics are also well know in the authorship verification and the information retrieval field.

\begin{definition}[Relevant link~\cite{kocher_linking}]
  A relevant link is a link in the relevant set.
  The relevant set is explained in Definition~\ref{def:relevant_set}.
  \begin{equation}
    relevant(l_i) =
    \begin{cases}
      1, & if\ l_i \in R \\
      0, & otherwise
    \end{cases}
  \end{equation}
\end{definition}

\begin{definition}[Precision@k~\cite{kocher_linking}]
  The precision@k is a function which take a positive integer k, with k < |L|
  \begin{equation}
    precision(k) = \frac{1}{k} \sum_{j=1}^{k} relevant(j)
  \end{equation}
\end{definition}

\begin{definition}[Average Precision (AP)]
  The mean over the precision@k each time a relevant link is retrieved.
  \begin{equation}
    AveragePrecision = \frac{1}{|R|} \sum_{j=1}^{|L|} precision(j) \cdot relevant(j)
  \end{equation}
  The average precision can be considered as an approximation of the area under the precision-recall curve.
\end{definition}

\begin{definition}[R-Precision~\cite{kocher_linking}]
  The R-Precision (RPrec) is the precision in the rank list at rank |R| (Precision@r).
  With R being the relevant set (Definition~\ref{def:relevant_set}).
  \begin{equation}
    RPrec = precision(|R|)
  \end{equation}
  The RPrec value is in the range $\left[0, 1\right]$.
  With 0 mean every link in the first $|R|$-ranks are not in the relevant set.
  And 1, every link in the first $|R|$-ranks are in the relevant set.
\end{definition}

\begin{definition}[High precision~\cite{kocher_linking}]
  The high precision (HPrec) represent the maximal rank j in the rank list such that the precision is still 100\%.
  \begin{equation}
    HPrec = \max\{i \in \mathbf{N} | precision(i) = 1\}
  \end{equation}
  This value is in the range $\left[0, |R|\right]$.
  $0$ means the first pair in the rank list is incorrect.
  $|R|$ means every true links are ranked in the top part of the rank list.
\end{definition}
