\section{Silhouette-based clustering\label{sec:silhouette-based_clustering}}

\subsection{Method}

The main idea of the Silhouette-based clustering is to evaluate in an unsupervised manner the clustering result for each number of clusters (at each merge step of the hierarchical clustering).
When discarding the clustering with $N$ and clusters $1$, this produce $N - 2$ possible clustering, each of those are evaluated using the mean Silhouette score.
The mean Silhouette score is defined in Definition~\ref{def:silhouette}.

\begin{definition}[Mean Silhouette score~\cite{sklearn}~\cite{wiki_silhouette}]
  \label{def:silhouette}
  The mean Silhouette score $s$ is an unsupervised clustering metric which evaluate a clustering result by measuring the cohesion $a(i)$ and separation of the clusters $b(i)$.

  \begin{gather*}
    s = \frac{1}{|C|} \sum_{i = 0}^{|C|} \frac{b(i) - a(i)}{max(a(i), b(i))}
  \end{gather*}
  \begin{gather*}
    \begin{split}
      a(i)&: \text{mean intra-cluster distance} \\
      a(i)& = \frac{1}{|C_i| - 1} \sum_{j \in C_i, i\neq j} d(i, j) \\
      b(i)&: \text{mean nearest-cluster distance} \\
      b(i)& = \min_{k\neq i} \frac{1}{|C_k|} \sum_{j \in C_k} d(i, j) \\
    \end{split}
  \end{gather*}
  With $C$ the set of clusters, $C_i$ the i-th cluster, $d(i, j)$ the distance between the document i and j.
  $d(i, j)$ are pre-computed and used for the rank list.

  The value is ranged between -1 and 1, a large value indicate a good cohesion and good separation of the clusters (low intra-cluster distance, high nearest-cluster distance).
\end{definition}

The right number of cluster is not known.
The idea is to apply the hierarchical clustering at each possible number of clusters (from $N - 1$ to $2$), and compute the mean Silhouette score.
The best clustering is the one with the largest mean Silhouette score.

An alternative to this method is the Iterative Positive Silhouette (IPS) and was proposed in Layton, Watters, Dazeley (2011)~\cite{automated_unsupervised}.
This method uses the median Silhouette score instead, and use another stopping procedure based on the sign of the score.

\subsection{Evaluation}

For this experiment, the goal is to test the Silhouette-based hierarchical clustering method based on the maximization of the mean Silhouette score on the literature corpora.

The rank list used for this experiment is the one from the retained text representation (9 for St-Jean and 7 for Brunet and Oxquarry), see Table~\ref{tab:rls_oxquarry_brunet}~and~\ref{tab:rls_st_jean} in annex.

The $B^3_{F_1}$ score and $r_{diff}$ average on the Silhouette-based clustering are presented in Table~\ref{tab:silhouette-based_clustering}, the complete table is available in Table~\ref{tab:silhouette-based_clustering_full} in annex.

The average r-ratio difference is a positive value ranging between $\left[0.17, 0.22\right]$ depending on the linkage criterion.
Having a too large r-ratio indicate that the estimated number of cluster on every corpus is overestimated.
This means that the mean neareast-cluster distance is greater than the mean intra-cluster distance, even when dealing with the right number of clusters.
In Table~\ref{tab:silhouette-based_clustering}, the r-ratio is clearly too high, and can be due to the fact that the rank list used for the clustering is not perfect (AP $\neq 1$).

\begin{table}
  \centering
  \caption{Silhouette-based clustering evaluation on retained rank lists, mean $B^3_{F_1}$/$r_{diff}$, Maximal Silhouette ($\alpha = 0$)}
  \label{tab:silhouette-based_clustering}

  \resizebox{\linewidth}{!}{
  \begin{tabular}{l c c c}
    \toprule
           & \multicolumn{3}{c}{Linkage criterion} \\
    Corpus    & Single     & Average   & Complete \\
    \midrule
    Oxquarry  & 0.76/0.18 & 0.79/0.12 & 0.78/0.13 \\
    Brunet    & 0.69/0.28 & 0.71/0.26 & 0.73/0.23 \\
    St-Jean A & 0.59/0.33 & 0.64/0.24 & 0.61/0.26 \\
    St-Jean B & 0.91/0.08 & 0.91/0.06 & 0.90/0.06 \\
    \midrule
    Absolute mean & 0.74/0.22 & 0.76/0.17 & 0.75/0.17 \\
    \midrule
    \textit{Upper bound} & \textit{0.83/0.00} & \textit{0.88/0.00} & \textit{0.87/0.00} \\
    \bottomrule
  \end{tabular}
  }
\end{table}

\subsection{Tweak for Authorship Clustering}

We want to mitigate having the number of cluster overestimated by the Silhouette-based clustering method.
An easy solution is to use the labels produced by the clustering earlier in the procedure (less merges, less clusters).
This corresponds to a non-maximal value of the mean Silhouette score, on the left side of the maximal mean Silhouette score.

In this study, we introduce a parameter called $\alpha$.
$\alpha$ represents a percentage to subtract to the maximal mean Silhouette score to obtain a new target with a lower mean Silhouette score (instead of the maximal value).

The mean Silhouette score across the number of clusters is a concave function.
The new target, can thus be either on the left or on the right of the maximal mean Silhouette.
To remove this ambiguity, the sign of $\alpha$ indicate on which side of the maximal Silhouette score the target should be.

With $\alpha = 0$, this corresponds to the maximal mean Silhouette score.
With a negative $\alpha$ the left side is targeted and with a positive $\alpha$, the right side.

The clustering with the Silhouette score the closest to the target on the desired side is retained.

\begin{definition}[$\alpha$-Silhouette]
  The $\alpha$-Silhouette target score found by using the maximal Silhouette score as a baseline and is adjusted using a parameter called $\alpha$.
  \begin{gather*}
    \begin{aligned}
    target &= max(Scores) - |\alpha| \cdot max(Scores) \\
           &= max(Scores) \cdot (1 - |\alpha|)
    \end{aligned}
  \end{gather*}
\end{definition}

Example~\ref{ex:alpha_correction} show the $\alpha$ computation and usage.

For example, by using $\alpha = -0.2$, we aim to correct this overshoot and increase the quality of the clustering results.
This value was chosen by grid search to optimize the $B^3_{F_1}$.

Table~\ref{tab:silhouette-based_clustering_alpha} show the evaluation with $\alpha = -0.2$, the complete table is available in Table~\ref{tab:silhouette-based_clustering_alpha_full} in annex.
With this correction technique, in average the $r_{diff}$ is closer to 0 and the average $B^3_{F_1}$ is increased in average by 6\% across all the corpora.
Like for the upper bound, the average linkage criterion give the best results for this clustering method, its $B^3_{F_1}$ is in average 2\% better.

\begin{example}
  \centering
  \caption{$\alpha$ correction}
  \label{ex:alpha_correction}

  \subcaption{Silhouette Scores for each number of clusters}
  \begin{tabular}{r r}
    \toprule
    Number of clusters & Silhouette Score \\
    \midrule
    3 & 2.5 \\
    4 & 3.2 \\
    5 & 3.5 \\
    6 & 3.9 \\
    7 & 3.1 \\
    8 & 2.9 \\
    \bottomrule
  \end{tabular}

  \vspace{0.5cm}

  \subcaption{$\alpha$ computations}
  \raggedright
  with $max(Scores) = 3.9$ and $\alpha = -0.2$

  \begin{gather*}
    \begin{aligned}
    target &= 3.9 \cdot (1 - |-0.2|) \\
           &= 3.9 \cdot 0.8 \\
           &= 3.12
     \end{aligned}
   \end{gather*}

  \vspace{0.5cm}

  \subcaption{Clustering selection}
  Since $\alpha$ is negative, the left side of the maximal mean Silhouette is used (smaller number of clusters).

  Thus, the clustering on the left side with the closest Silhouette score to the target is the one with 4 clusters (score: 3.2).
\end{example}

\begin{table}
  \centering
  \caption{Silhouette-based clustering evaluation on retained rank lists, average  $B^3_{F_1}$/$r_{diff}$, $\alpha = -0.2$}
  \label{tab:silhouette-based_clustering_alpha}

  \resizebox{\linewidth}{!}{
  \begin{tabular}{l c c c}
    \toprule
           & \multicolumn{3}{c}{Linkage criterion} \\
    Corpus    & Single     & Average   & Complete \\
    \midrule
    Oxquarry  & 0.81/0.06 & 0.78/0.03 & 0.79/0.02 \\
    Brunet    & 0.78/0.10 & 0.80/0.09 & 0.80/0.10 \\
    St-Jean A & 0.70/0.14 & 0.77/0.08 & 0.76/0.09 \\
    St-Jean B & 0.86/0.02 & 0.87/0.03 & 0.86/0.03 \\
    \midrule
    Absolute mean & 0.79/0.08 & 0.81/0.06 & 0.80/0.06 \\
    \midrule
    \textit{Upper bound} & \textit{0.83/0.00} & \textit{0.88/0.00} & \textit{0.87/0.00} \\
    \bottomrule
  \end{tabular}
  }
\end{table}
